A Large and Variable Leading Tail of Helium in a Hot Saturn Undergoing Runaway Inflation

### 2023-09-18 paper/paper1/ms.tex
Revise Figure 14, related to Issue #45

\begin{figure}
  \includegraphics[width=0.8\linewidth]{KeplerianShear_v0p5_alt.png}
  \caption{Schematic of Keplerian orbital shear.  Locations outside the Roche lobe experience orbital shear from the Keplerian potential.  A wind launched primarily from the dayside will tend to form a leading tail.}
  \label{fig:KeplerianShear}
\end{figure}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=0.95\textwidth]{Fig14_KeplerianShear_revised.png}
  \caption{\edit1{A conceivable steady-state path of mass loss from the HAT-P-67~b system.  The inset depicts mass loss rates achieving maximum at the sub solar point, with a fall off towards zero near the planet terminator.  The small Roche lobe of merely $<2.7R_p$ means that gas promptly experiences Keplerian orbital shear after launching past the L1 point.}  A wind launched primarily from the dayside will tend to form a leading tail.  \edit1{The orbital overview depicts the path of the mass loss initially towards the star, decelerating into the headwind of the stellar wind, and then reversing direction outward in a blueshift. The observed redshift and blueshift of any given sightline will depend on the Helium ionization fraction, which depends on the shielding of gas along the line of sight.} }
  \label{fig:KeplerianShear}
\end{figure*}
